---
title: "Instacart Orders in the Witching Hours"
author: "Laura Cosgrove"
date: "10/28/2018"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(plotly)
library(p8105.datasets)
library(flexdashboard)
```
In the spirit of Halloween and midterm season, let's filter the Instacart data to look specifically at orders placed between midnight and 4 a.m. -- by far the least popular times to order groceries on Instacart.

```{r data, include = FALSE}
data(instacart)

instacart <- instacart %>%
 filter(order_hour_of_day <= 4) 

```



Column {data-width=600}
----------------------------------------------------------------------

### Popular Departments

Among late-night orderers who ordered just a few items, what were the most popular departments and aisles?

```{r plotly column plot}
instacart %>%
  group_by(order_id) %>% 
  add_tally() %>% 
  filter(n < 4) %>% 
  select(order_id, product_id, product_name, order_dow, order_hour_of_day, days_since_prior_order, aisle, department, n) %>%
  ungroup() %>% 
  group_by(department) %>% 
  add_tally() %>% 
  ungroup() %>% 
  mutate(department = forcats::fct_reorder(department, nn)) %>% 
  mutate(aisle = forcats::fct_reorder(aisle, nn)) %>% 
  plot_ly(y = ~department, x = ~nn, color = ~aisle, type = "bar") %>% 
  layout(barmode = "stack")

```

Column {data-width=400}
-----------------------------------------------------------------------

### Popular Times to Order

When are the most items ordered, by day of week and hour of day?

```{r plotly heat map}
instacart %>% 
  group_by(order_hour_of_day, order_dow) %>% 
  add_tally() %>% 
  ungroup() %>% 
  mutate(order_dow = factor(order_dow, levels = 0:6, labels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) %>%
  plot_ly(x = ~ order_dow, y = ~order_hour_of_day, z = ~n, type = "heatmap") %>% 
  layout(xaxis = list(title = "Day of Week"), 
         yaxis = list(title = "Hour of Day"), 
         showlegend = FALSE)
```

### Quantity of Products Ordered, by Days Since Last Order

Does quantity of products in a single order change based on days since last order? 

```{r plotly box plot}

instacart %>%
  group_by(days_since_prior_order, order_id) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(days_since_prior_order = factor(cut_interval(days_since_prior_order, length = 7))) %>% 
  plot_ly(color = ~ days_since_prior_order, y = ~n, type = "box") %>% 
  add_annotations( text="Days", xref="paper", yref="paper",
                  x=1.02, xanchor="left",
                  y=0.8, yanchor="bottom",   
                  legendtitle=TRUE, showarrow=FALSE ) %>%
  layout(legend=list(y=0.8, yanchor="top" ) )  
```
