---
title: "Instacart Orders in the Witching Hours"
author: "Laura Cosgrove"
date: "10/28/2018"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(plotly)
library(p8105.datasets)
library(flexdashboard)
```
In the spirit of Halloween and midterm season, let's filter the Instacart data to look specifically at orders placed between midnight and 4 a.m. -- by far the least popular times to order groceries on Instacart.

```{r data, include = FALSE}
data(instacart)

instacart <- instacart %>%
 filter(order_hour_of_day <= 5) 

```



Column {data-width=650}
----------------------------------------------------------------------

### Chart A

Among late-night orderers who ordered just a few items, what were the most popular departments and aisles?

```{r plotly columb plot}
instacart %>%
  group_by(order_id) %>% 
  add_tally() %>% 
  filter(n < 4) %>% 
  select(order_id, product_id, product_name, order_dow, order_hour_of_day, days_since_prior_order, aisle, department, n) %>%
  ungroup() %>% 
  group_by(department) %>% 
  add_tally() %>% 
  ungroup() %>% 
  mutate(department = forcats::fct_reorder(department, nn)) %>% 
  plot_ly(y = ~department, x = ~nn, color = ~aisle, type = "bar") %>% 
  layout(barmode = "stack")

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

When are the highest-volume orders, by day of week and hour of day?

```{r plotly heat map}
instacart %>% 
  group_by(order_id) %>% 
  add_tally() %>% 
  plot_ly(x = ~ order_dow, y = ~order_hour_of_day, z = ~n, type = "heatmap")

```

### Chart C

How frequent Instacart orderers are these late-night orderers?

```{r plotly box plot}

instacart %>%
  group_by(days_since_prior_order, order_id) %>% 
  tally() %>% 
  plot_ly(x = ~ days_since_prior_order, y = ~n, type = "box")
  
```
